tikz

### 2023-12-18 Misc/Visuals_Interactives/alm_gg.qmd
big sync

library(ggplot2)
library(patchwork)
library(dplyr)

@@

>>>>

```{r}
#| eval: false
#| 
library(ggplot2)
library(patchwork)
library(dplyr)

@@

library(ggplot2)
library(tidyr)

# Define the matrix size
n_rows <- 8
n_cols <- 10

# Create an empty matrix
category_matrix <- matrix(NA, n_rows, n_cols)

# Fill the matrix based on the figure
# 1 for rule training instances and 2 for exceptions
category_matrix[1:4, 1:2] <- 1
category_matrix[5:8, 1:2] <- 2
category_matrix[1:2, 3:10] <- 2
category_matrix[3:4, 3:10] <- 1
category_matrix[5:6, 3:10] <- 1
category_matrix[7:8, 3:10] <- 2

# Convert the matrix to a tidy data frame for plotting
category_df <- as.data.frame(as.table(category_matrix))

# Plot
ggplot(category_df, aes(x=Var2, y=-Var1)) +
  geom_tile(aes(fill=factor(category_matrix)), color="black") +
  scale_fill_manual(values=c("black", "white")) +
  theme_minimal() +
  labs(fill="Category", 
       title="Category Structure for Experiment 2",
       x="Segment Position", 
       y="Rectangle Height")

```{r}
#| eval: false
library(tidyverse)

# Define the architecture

# Rule Module
rule_module <- function(input, weights) {
  # Activate rule nodes based on the input and boundary
  activated_rule <- ifelse(input > some_boundary_value, 1, 0) # some_boundary_value needs to be defined
  return(activated_rule * weights)
}

# Exemplar Module (ALCOVE)
exemplar_module <- function(input, exemplars, attention_weights, exemplar_weights) {
  # Compute similarity between input and each exemplar
  similarity <- rowSums((input - exemplars)^2 * attention_weights)
  activations <- exp(-similarity)

  # Compute category response
  response <- sum(activations * exemplar_weights)

  return(response)
}

# Gating Mechanism
gating_mechanism <- function(rule_output, exemplar_output, g) {
  return(g * rule_output + (1 - g) * exemplar_output)
}

# Initialize parameters
rule_weights <- runif(2)  # Example weights for the rule module, actual initialization may differ
exemplars <- matrix(runif(10), ncol=2)  # Assuming 5 exemplars with 2-dimensional input for demonstration purposes
attention_weights <- runif(2)  # Example attention weights
exemplar_weights <- runif(5)  # Example weights for the exemplar module
g <- 0.5  # Example gating parameter, the actual value should be set based on the model

# Simulate the model with an input
input_data <- c(0.5, 0.5)  # Example 2-dimensional input

rule_output <- rule_module(input_data, rule_weights)
exemplar_output <- exemplar_module(input_data, exemplars, attention_weights, exemplar_weights)
final_output <- gating_mechanism(rule_output, exemplar_output, g)

print(final_output)
